---
title: "free2playR Package"
author: "Lasse Rodeck"
date: "`r Sys.Date()`"
output: 
  html_document:
    css: custom.css
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(colorspace)
library(DiagrammeR)
library(kableExtra)

ggthemr::ggthemr("pale")
extrafont::loadfonts(device = "win")

ggthemr::ggthemr("pale")
```

## **Introduction**

This document demonstrates the use of the MyGamePackage framework for simulating a farming game feature. The player plants, grows, and harvests crops, manages resources, and upgrades farming equipment to improve efficiency.

## **Load MyGamePackage**

```{r load_package, echo=TRUE, message=FALSE, warning=FALSE}
# Load the package
library(free2playR)
```

## **Initialize the User**

Initialize the user with some initial resources and attributes.

```{r initialize_user, echo=TRUE, message=FALSE, warning=FALSE}
# Initialize the user
user <- initialize_user(
  user_id = 1,
  initial_currency1 = 1000,  # Gold
  initial_currency2 = 500,   # Water
  initial_public_order = 50,
  initial_happiness = 50,
  initial_xp = 0,
  initial_level = 1,
  tech_nodes = c("UpgradeHoe1", "UpgradeHoe2", "UpgradeWateringCan1", "UpgradeWateringCan2")
)
user %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## **Define Tech Nodes for Upgrading Equipment**

Define tech nodes for upgrading the farming equipment.

```{r define_tech_nodes, echo=TRUE, message=FALSE, warning=FALSE}
# Define tech nodes for upgrading equipment
upgrade_hoe1 <- define_tech_node(
  node_name = "UpgradeHoe1",
  cost_currency1 = 100,
  cost_currency2 = 50,
  time_required = 2,
  value = 1,
  xp_reward = 50
)

upgrade_hoe2 <- define_tech_node(
  node_name = "UpgradeHoe2",
  cost_currency1 = 200,
  cost_currency2 = 100,
  time_required = 3,
  value = 2,
  xp_reward = 100,
  prerequisites = "UpgradeHoe1",
  level_requirement = 2
)

upgrade_watering_can1 <- define_tech_node(
  node_name = "UpgradeWateringCan1",
  cost_currency1 = 150,
  cost_currency2 = 75,
  time_required = 2,
  value = 1,
  xp_reward = 60
)

upgrade_watering_can2 <- define_tech_node(
  node_name = "UpgradeWateringCan2",
  cost_currency1 = 300,
  cost_currency2 = 150,
  time_required = 3,
  value = 2,
  xp_reward = 120,
  prerequisites = "UpgradeWateringCan1",
  level_requirement = 2
)

```

## **Define the Tech Tree**

Define the tech tree with the created tech nodes.

```{r define_tech_tree, echo=TRUE}
# Define the tech tree
tech_tree <- define_tech_tree(upgrade_hoe1, upgrade_hoe2, upgrade_watering_can1, upgrade_watering_can2)
tech_tree %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## **Define Actions for Planting, Growing, and Harvesting Crops**

Define actions for planting, growing, and harvesting crops.

```{r define_actions, echo=TRUE}
# Define actions for planting, growing, and harvesting crops
# Define actions for planting, growing, and harvesting crops
plant_wheat <- define_action(
  action_name = "PlantWheat",
  cost_currency1 = 50,  # Cost in gold
  cost_currency2 = 20,  # Cost in water
  perceived_value = 5,
  public_order_change = 1,
  happiness_change = 1,
  xp_reward = 30,
  level_requirement = 1
)

grow_wheat <- define_action(
  action_name = "GrowWheat",
  cost_currency1 = 10,
  cost_currency2 = 10,
  perceived_value = 10,
  public_order_change = 1,
  happiness_change = 2,
  xp_reward = 50,
  level_requirement = 1
)

harvest_wheat <- define_action(
  action_name = "HarvestWheat",
  cost_currency1 = 0,
  cost_currency2 = 0,
  perceived_value = 20,
  public_order_change = 2,
  happiness_change = 3,
  xp_reward = 100,
  level_requirement = 1
)
list(plant_wheat, grow_wheat, harvest_wheat) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## **Define Quests for Completing Farming Tasks**

Define quests for completing farming tasks.

```{r define_quest, echo=TRUE, message=FALSE, warning=FALSE}
# Define quests for completing farming tasks
quest_plant_wheat <- define_quest(
  quest_name = "QuestPlantWheat",
  requirement = 30,  # XP requirement to complete the quest
  reward_currency1 = 50,  # Gold reward
  reward_currency2 = 30,   # Water reward
  reward_xp = 50
)

quest_harvest_wheat <- define_quest(
  quest_name = "QuestHarvestWheat",
  requirement = 100,
  reward_currency1 = 100,
  reward_currency2 = 50,
  reward_xp = 100
)
rbind(quest_plant_wheat, quest_harvest_wheat) %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

## **Simulate Actions and Quests**

Simulate the player's actions of planting, growing, and harvesting crops, and completing quests to manage the farm.

```{r simulate_actions, echo=TRUE, message=FALSE, warning=FALSE}
# Data frame to store user progress for visualization
progress_df <- tibble(
  step = integer(),
  action = character(),
  currency1 = numeric(),
  currency2 = numeric(),
  xp = numeric(),
  level = numeric(),
  tech_progress = list()
)

# Helper function to log progress
log_progress <- function(step, action_name, user) {
  progress_df <<- progress_df %>% add_row(
    step = step,
    action = action_name,
    currency1 = user$currency1[1],
    currency2 = user$currency2[1],
    xp = user$xp[1],
    level = user$level[1],
    tech_progress = list(user$tech_progress[[1]])
  )
}


# Simulate planting wheat
user <- simulate_action(user, plant_wheat)
log_progress(1, "PlantWheat", user)

# Simulate growing wheat
user <- simulate_action(user, grow_wheat)
log_progress(2, "GrowWheat", user)

# Simulate harvesting wheat
user <- simulate_action(user, harvest_wheat)
log_progress(3, "HarvestWheat", user)

# Simulate upgrading the equipment
user <- simulate_tech_progression(user, tech_tree)
log_progress(4, "UpgradeEquipment", user)

# Simulate completing the quest to plant wheat
user <- complete_quest(user, quest_plant_wheat)
log_progress(5, "CompleteQuestPlantWheat", user)

# Simulate completing the quest to harvest wheat
user <- complete_quest(user, quest_harvest_wheat)
log_progress(6, "CompleteQuestHarvestWheat", user)

# Display progress_df as a formatted HTML table
progress_df %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

```

## **Visualize the Results**

Visualize the changes in user attributes like gold, water, XP, and the progress in tech upgrades over time.

```{r visualize_results, echo=FALSE, message=FALSE, warning=FALSE}

# Plot gold and water over time
p1 <- ggplot(progress_df, aes(x = step)) +
  geom_line(aes(y = currency1, color = "Gold")) +
  geom_line(aes(y = currency2, color = "Water")) +
  labs(title = "Gold and Water Over Time", x = "Step", y = "Amount", color = "Resource") +
    theme(text = element_text(family = "Inter", colour = "#0C0C0C")
          , plot.title = element_text(size = 14, face = "bold")
          , plot.subtitle = element_text(size = 10)
          , plot.caption = element_text(size = 8)
          , axis.text = element_text(size = 8)
          , axis.title = element_text(size = 10)
          , legend.text = element_text(size = 8)
          , legend.title = element_text(size = 10, face = "bold")
          , strip.text = element_text(size = 8, face = "bold")
          , legend.position = "top"
          , legend.direction = "horizontal"
          , legend.justification = "left"
          , panel.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , plot.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , panel.grid.major = element_line(color = "#F0F0F0") # Set major grid lines to Light Gray
          , panel.grid.minor = element_blank() # Remove minor grid lines
          , strip.background = element_rect(fill = "#F8F8FF") # Set facet background color to Ghost White
          , legend.background = element_rect(fill = "#F8F8FF", color = NA) # Set legend background color to Ghost White
          , legend.key = element_blank() # Remove legend key
    )

# Plot XP and level over time
p2 <- ggplot(progress_df, aes(x = step)) +
  geom_line(aes(y = xp, color = "XP")) +
  labs(title = "XP Over Time", x = "Step", y = "XP", color = "Attribute") +
    theme(text = element_text(family = "Inter", colour = "#0C0C0C")
          , plot.title = element_text(size = 14, face = "bold")
          , plot.subtitle = element_text(size = 10)
          , plot.caption = element_text(size = 8)
          , axis.text = element_text(size = 8)
          , axis.title = element_text(size = 10)
          , legend.text = element_text(size = 8)
          , legend.title = element_text(size = 10, face = "bold")
          , strip.text = element_text(size = 8, face = "bold")
          , legend.position = "top"
          , legend.direction = "horizontal"
          , legend.justification = "left"
          , panel.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , plot.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , panel.grid.major = element_line(color = "#F0F0F0") # Set major grid lines to Light Gray
          , panel.grid.minor = element_blank() # Remove minor grid lines
          , strip.background = element_rect(fill = "#F8F8FF") # Set facet background color to Ghost White
          , legend.background = element_rect(fill = "#F8F8FF", color = NA) # Set legend background color to Ghost White
          , legend.key = element_blank() # Remove legend key
    )

# Plot XP and level over time
p3 <- ggplot(progress_df, aes(x = step)) +
  geom_line(aes(y = level, color = "Level")) +
  labs(title = "Level Over Time", x = "Step", y = "Level", color = "Attribute") +
    theme(text = element_text(family = "Inter", colour = "#0C0C0C")
          , plot.title = element_text(size = 14, face = "bold")
          , plot.subtitle = element_text(size = 10)
          , plot.caption = element_text(size = 8)
          , axis.text = element_text(size = 8)
          , axis.title = element_text(size = 10)
          , legend.text = element_text(size = 8)
          , legend.title = element_text(size = 10, face = "bold")
          , strip.text = element_text(size = 8, face = "bold")
          , legend.position = "top"
          , legend.direction = "horizontal"
          , legend.justification = "left"
          , panel.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , plot.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , panel.grid.major = element_line(color = "#F0F0F0") # Set major grid lines to Light Gray
          , panel.grid.minor = element_blank() # Remove minor grid lines
          , strip.background = element_rect(fill = "#F8F8FF") # Set facet background color to Ghost White
          , legend.background = element_rect(fill = "#F8F8FF", color = NA) # Set legend background color to Ghost White
          , legend.key = element_blank() # Remove legend key
    )

gridExtra::grid.arrange(p1,p2,p3)

```

Additionally we can also plot out the actions and the development of user stats.

```{r flow, echo=FALSE, message=FALSE, warning=FALSE}
# Plot sequence of actions over time
ggplot(progress_df, aes(x = step, y = currency1, group = 1)) +
  geom_line() +
  geom_point() +
  geom_label(aes(label = action)) +
  labs(title = "Sequence of Actions Over Time", x = "Step", y = "Gold") +
  theme(text = element_text(family = "Inter", colour = "#0C0C0C")
          , plot.title = element_text(size = 14, face = "bold")
          , plot.subtitle = element_text(size = 10)
          , plot.caption = element_text(size = 8)
          , axis.text = element_text(size = 8)
          , axis.title = element_text(size = 10)
          , legend.text = element_text(size = 8)
          , legend.title = element_text(size = 10, face = "bold")
          , strip.text = element_text(size = 8, face = "bold")
          , legend.position = "top"
          , legend.direction = "horizontal"
          , legend.justification = "left"
          , panel.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , plot.background = element_rect(fill = "#F8F8FF") # Set background color to Ghost White
          , panel.grid.major = element_line(color = "#F0F0F0") # Set major grid lines to Light Gray
          , panel.grid.minor = element_blank() # Remove minor grid lines
          , strip.background = element_rect(fill = "#F8F8FF") # Set facet background color to Ghost White
          , legend.background = element_rect(fill = "#F8F8FF", color = NA) # Set legend background color to Ghost White
          , legend.key = element_blank() # Remove legend key
    )


```

## **Visualize the Tech Tree as a Tree Diagram**

Visualize the tech tree as a tree diagram using the **`DiagrammeR`** package.

```{r tree, echo=FALSE, message=FALSE, warning=FALSE}
library(DiagrammeR)
# Create a node graph for the tech tree
graph <- create_graph()

# Add nodes to the graph
for (i in seq_len(nrow(tech_tree))) {
  node <- tech_tree$node[[i]]
  graph <- add_node(graph, label = node$node_name, type = "tech_node")
}

# Add edges based on prerequisites
for (i in seq_len(nrow(tech_tree))) {
  node <- tech_tree$node[[i]]
  if (!is.null(node$prerequisites)) {
    for (prereq in unlist(node$prerequisites)) {
      graph <- add_edge(graph, from = prereq, to = node$node_name)
    }
  }
}

# Render the graph
render_graph(graph, layout = "tree", output = "visNetwork")
```

## **Conclusion**

This example demonstrates how to use the free2playR framework to simulate a farming game feature. The player plants, grows, and harvests crops, manages resources, and upgrades farming equipment to improve efficiency.
